% CHENG TZE KEONG ATS-Compatible Resume (LaTeX)
\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{xcolor}

% Formatting
\titleformat{\section}{\normalfont\Large\bfseries\color{black}}{}{0em}{}
\titleformat{\subsection}{\normalfont\bfseries}{}{0em}{}
\renewcommand{\labelitemi}{--}
\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=blue
}

\begin{document}

% ===== Header =====
\begin{center}
    {\LARGE\textbf{CHENG TZE KEONG}} \\
    \href{mailto:johnmelodymel@qq.com}{johnmelodymel@qq.com} $\mid$ +6013-739-7193 $\mid$ \href{https://www.ctkqiang.xin}{ctkqiang.xin}
\end{center}

% ===== Objective =====
\section*{Objective}
Senior Software Engineer with expertise in full-stack development, mobile applications, and cybersecurity, seeking a role in AI to develop innovative and scalable software solutions.

% ===== Skills =====
\section*{Skills and Abilities}
\subsection*{Technical Skills}
\textbf{Languages:} Java, Swift, Python, Golang, PHP, Dart, COBOL, Erlang, Elixir, C/C++, JavaScript, TypeScript, Zig, Bash, Cangjie \\
\textbf{Front-End:} Flutter, SwiftUI, WeChat Mini Program, HBuilder, VueJS, ArkTS(for Harmony OS), Next.js, TailwindCSS, TDesign \\
\textbf{Back-End:} Node.js, Express.js, NestJS, FastAPI, Phoenix (Elixir), Rebar (Erlang), GraphQL, gRPC, Spring Boot (Java), Gin Golang, Laravel PHP, FastAPI Python, Java Servlet (for old corporate Projects) \\
\textbf{Databases:} MySQL, OracleDB, Firestore, CouchDB, MongoDB, Redis, Supabase \\
\textbf{AI/ML:} TensorFlow, PyTorch, OpenCV, Hugging Face, NLP, LLMs, Transformer \\
\textbf{Blockchain:} Solidity, Smart Contracts, XRP sdk, TON, IPFS, DeFi, dApps

\subsection*{Soft Skills}
Problem-solving, Team Leadership, Communication, Project Management, Time Management

% ===== Experience =====
\section*{Professional Experience}
\subsection*{Senior Full-Stack Developer \\ \normalfont Freelance \hfill Aug 2023 -- Present}
\begin{itemize}[leftmargin=1.5em]
    \item Built intelligent NLP-based customer service systems, reducing manual load by 40\%.
    \item Developed Cyber security tools for Red Team and White Team (Refer github)
    \item Applied ML for predictive modeling in healthcare.
    \item Developed ERP backends with Spring Boot.
    \item Designed cross-chain DeFi payments (Stripe + crypto), 5000 TPS.
    \item Performed pentesting for medical firms, achieving ISO 27001 compliance.
    \item Created Assembly x64, C/C++ system monitoring tools and Arduino-based IDS.
\end{itemize}

\subsection*{Senior Mobile Application Developer \\ \normalfont Sleekflow Private Limited \hfill Aug 2022 -- Dec 2023}
\begin{itemize}[leftmargin=1.5em]
    \item Delivered new eCommerce app features with payment integration.
    \item Used WhatsApp API and Wechat API, Stripe. (Service)
    \item Flutter, Swift, Kotlin. (Client)
    \itme Redis, MySQL, Kafka, Spring Boot (Backend)
\end{itemize}

\subsection*{Senior Software Engineer \\ \normalfont Mynapse Sdn Bhd \hfill Apr 2020 -- Jun 2022}
\begin{itemize}[leftmargin=1.5em]
    \item Developed SMS services, SIP realtime voice and (Webrtc-Janus) real-time video calls.
    \item Used Kotlin, Java, Flutter (Client).
    \item Elixir, Erlang, CouchDB (Backend).
\end{itemize}

\subsection*{Software Engineer \\ \normalfont Braintech (M) Sdn Bhd \hfill Jan 2018 -- Mar 2020}
\begin{itemize}[leftmargin=1.5em]
    \item Created EEG/BCI scientific software.
    \item Integrated Nordic & Qualcomm SDK in Android (Java and C/C++).
    \item Built Firebase/MySQL-powered services.
\end{itemize}

\subsection*{Armed Security Guard \\ \normalfont G4S \hfill Jun 2014 -- Nov 2017}
\begin{itemize}[leftmargin=1.5em]
    \item Maintained facility and data security.
    \item Operated identification and access control systems.
\end{itemize}

% ===== Education =====
\section*{Education}
\textbf{SMK Hamid Khan} \hfill Malaysian Higher School Certificate (2013) \\
Internships in sports organizations, event planning, and sponsorship coordination.

\end{document}
